%The study of the network traffic patterns began with tools that utilized raw
%packet captures at the monitoring point for traffic measurement.
%\texttt{tcpdump} and \texttt{wireshark} have since then become the de-facto
%tools for packet capture and analysis. \texttt{tcpdump} \cite{tcpdump-manpage}
%is a premier command-line utility that uses the \texttt{libpcap}
%\cite{pcap-manpage} library for packet capture. The power of \texttt{tcpdump}
%comes from the richness of its expressions, the ability to combine them using
%logical connectives and extract specific portions of a packet using filters.
%\texttt{wireshark} \cite{wireshark-manpage} is a GUI application, aimed at
%both journeymen and packet analysis experts. It supports a large number of
%protocols, has a straightforward layout, excellent documentation, and can run
%on all major operating systems.

In recent years, a number of tools have been developed that can capture the
traffic as flow records and use them for network analysis. \texttt{flow-tools}
and \texttt{nfdump} are among the most popular tools used for analyzing
NetFlow data. \texttt{flow-tools} \cite{sromig:2000} is a suite of programs
for capturing and processing NetFlow v5 flow records. It consists of 24
separate tools that work together by connecting them via UNIX pipes. It can
capture, read, filter, and print flow records internally saved in a fixed-size
format. \texttt{nfdump} \cite{phaag:2006} is a very similar tool that uses a
different storage format. Flow records are captured using \texttt{nfcapd} and
then processed by \texttt{nfdump}. The power of filtering rules in both the
tools is however mostly limited to absolute comparisons of flow attributes. As
a result, relative comparison amongst different flows or querying a timing
relationship among them is not possible.  SiLK \cite{SiLK} is a network
traffic collection and analysis tool developed and maintained by the CERT
Network Situational Awareness Team (CERT NetSA) at Carnegie Mellon University.
SiLK is the tool that comes quite close to providing similar capabilities as
provided by \ac{NFQL} and is therefore used as a reference point to compare
the performance of the \ac{NFQL} execution engine in this paper. The design
and implementation of SiLK, however, differs a lot from that of \ac{NFQL}. For
instance, in SiLK there are separate tools to perform the task of each stage
of the \ac{NFQL} processing pipeline. The stage functionality is not
full-fledged though. The grouping and merging operations can only be performed
using an equality operator. This restriction allows the tool to perform
optimization such as using hash tables to perform lookups. There are also
stringent requirements to how flow-data needs to be organized before it can be
piped into a tool. The grouping tool, for instance, assumes that the to-be
supplied input flow data is already sorted on the field column.  These
requirements can make it a little cumbersome to design a full-fledged flow
query.  For instance, trying to mimic a \ac{NFQL} query in SiLK sometimes ends
up as a shell script with over a dozen of SiLK tools piped together.
